---
title: "Challenge-3"
author: "Annette"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## I. Questions

#### Question 1: Emoji Expressions

Imagine you're analyzing social media posts for sentiment analysis. If you were to create a variable named "postSentiment" to store the sentiment of a post using emojis ( for positive,  for neutral,  for negative), what data type would you assign to this variable? Why? (_narrative type question, no code required_)

**Solution:**  I would use data type "string" because emojis are a form of textual representation composed of Unicode characters. Strings can accommodate sequences of characters and thus they are a sutiable data type for storing emojis used to indicate sentiment. By using string data type I will be able to store and manipuate my emojis within the variable.


#### Question 2: Hashtag Havoc

In a study on trending hashtags, you want to store the list of hashtags associated with a post. What data type would you choose for the variable "postHashtags"? How might this data type help you analyze and categorize the hashtags later? (_narrative type question, no code required_)

**Solution:**  I would use "list of strings". This is because this data type allows for structured storage for maintaining the hashtag order in each post. It also allows for easy access to individuals element by index, and can also perform analysis on each hashtag individually such as counting the frequency, categorsingby topic, and filtering.


#### Question 3: Time Traveler's Log
  
You're examining the timing of user interactions on a website. Would you use a numeric or non-numeric data type to represent the timestamp of each interaction? Explain your choice (_narrative type question, no code required_)

**Solution:**  I would use a data type like "Datetime" or "Timestamp", as it can accurately store both the date and time of each interaction and their respective parts, down to the milliseconds. Furthermore, I can manipulate, sort, and format the data which will be advantageous for analysis. 


#### Question 4: Event Elegance

You're managing an event database that includes the date and time of each session. What data type(s) would you use to represent the session date and time? (_narrative type question, no code required_)

**Solution:**  I would use "Datetime" as it allows me to view both the date and time in a single values, and I can perform calculations, comparisons and sorting, to analyse my different events on both date and time values. This makes my analysis more efficient and convenient.

#### Question 5: Nominee Nominations
You're analyzing nominations for an online award. Each participant can nominate multiple candidates. What data type would be suitable for storing the list of nominated candidates for each participant?  (_narrative type question, no code required_)

**Solution:**  I would use a list or an array. This is because the structure of a list or array allows me to capture the multiple candidates that is associate with each participant in the nomination. Later on, I can perform analysis on the data to identify the popular candidates and more.

#### Question 6: Communication Channels
In a survey about preferred communication channels, respondents choose from options like "email," "phone," or "social media." What data type would you assign to the variable "preferredChannel"? (_narrative type question, no code required_)

**Solution:**  I would use a categorical or nominal data type. This is becasue the values are discrete as there are only a few set options, and there is no order or numerical value associated with them.

#### Question 7: Colorful Commentary

In a design feedback survey, participants are asked to describe their feelings about a website using color names (e.g., "warm red," "cool blue"). What data type would you choose for the variable "feedbackColor"? (_narrative type question, no code required_)

**Solution:**  I woud use a "string" data type. This is because the colour names are made out of characters, and participants may provide a wide variety of descriptive answers. This data type will be able to store the textual data without imposing any constraints on the content.

#### Question 8: Variable Exploration

Imagine you're conducting a study on social media usage. Identify three variables related to this study, and specify their data types in R. Classify each variable as either numeric or non-numeric.

**Solution:**  The first variable would be time spent on social media, and it is a numeric data type. The next variable is the hashtags used, which is a non-numeric data type. Lastly is the count of the likes on posts, which is a numeric data type.

#### Question 9: Vector Variety

Create a numeric vector named "ages" containing the ages of five people: 25, 30, 22, 28, and 33. Print the vector.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
ages <- c(25,30,22,28,33)
print(ages)
```

#### Question 10: List Logic

Construct a list named "student_info" that contains the following elements:

  - A character vector of student names: "Alice," "Bob," "Catherine"

  - A numeric vector of their respective scores: 85, 92, 78

  - A logical vector indicating if they passed the exam: TRUE, TRUE, FALSE

Print the list.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
student_info <- list(names = c("Alice", "Bob", "Catherine"), scores = c(85, 92, 78), passed = c(TRUE, TRUE, FALSE))

student_info
```

#### Question 11: Type Tracking

You have a vector "data" containing the values 10, 15.5, "20", and TRUE. Determine the data types of each element using the typeof() function.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
data <- c(10, 15.5, "20", TRUE)
typeof(data[1])
typeof(data[2])
typeof(data[3])
typeof(data[4])
```

#### Question 12: Coercion Chronicles

You have a numeric vector "prices" with values 20.5, 15, and "25". Use explicit coercion to convert the last element to a numeric data type. Print the updated vector.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
prices <- c(20.5, 15, "25")
prices <- as.numeric(prices)
print(prices)
```

#### Question 13: Implicit Intuition

Combine the numeric vector c(5, 10, 15) with the character vector c("apple", "banana", "cherry"). What happens to the data types of the combined vector? Explain the concept of implicit coercion.

**Solution:** Initially,x and y vectors are "double" and "character" respectively. When I combine them, R will perform implicit coercion to accommodate both types of data in the new vector. In this case, the numeric data types were converted to character strings, since characters can represent both numbers and text.

```{r, eval=TRUE,echo=TRUE}
x <- c(5, 10,15)
typeof(x)
y <- c("apple", "banana", "cherry")
typeof(y)
combined_vector <- c(5, 10, 15, "apple", "banana", "cherry")
typeof(combined_vector)
```

#### Question 14: Coercion Challenges

You have a vector "numbers" with values 7, 12.5, and "15.7". Calculate the sum of these numbers. Will R automatically handle the data type conversion? If not, how would you handle it?

**Solution:** R does not automatically handle the data type conversion. I will use the 'as.numeric()' function.

```{r, eval=TRUE,echo=TRUE}
numbers <- c(7, 12.5, "15.7")
numbers <- as.numeric(numbers)
sum_result <- sum(numbers)
print(sum_result)
```

#### Question 15: Coercion Consequences

Suppose you want to calculate the average of a vector "grades" with values 85, 90.5, and "75.2". If you directly calculate the mean using the mean() function, what result do you expect? How might you ensure accurate calculation?

**Solution:** I expect an error as not all my data is numeric. I will use "as.numeric()" function to convert the character values, then use the "mean()" function.

```{r, eval=TRUE,echo=TRUE}
grades <- c(85, 90.5, "75.2")
grades <- as.numeric(grades)
mean(grades)
```

#### Question 16: Data Diversity in Lists

Create a list named "mixed_data" with the following components:

  - A numeric vector: 10, 20, 30
  
  - A character vector: "red", "green", "blue"

  - A logical vector: TRUE, FALSE, TRUE
  
Calculate the mean of the numeric vector within the list.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
mixed_data <- list( numeric_vector <- c(10,20,30), character_vector <- c("red","green","blue"), logical_vector <- c(TRUE, FALSE, TRUE))

mean(numeric_vector)
```

#### Question 17: List Logic Follow-up

Using the "student_info" list from Question 10, extract and print the score of the student named "Bob."

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
student_info <- list(names = c("Alice", "Bob", "Catherine"), scores = c(85, 92, 78), passed = c(TRUE, TRUE, FALSE))
bob_score <- student_info$scores[student_info$names == "Bob"]
print(bob_score)
```

#### Question 18: Dynamic Access

Create a numeric vector values with random values. Write R code to dynamically access and print the last element of the vector, regardless of its length.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
x <- double(23)
last_element <- x[length(x)]
print(last_element)
```

#### Question 19: Multiple Matches

You have a character vector words <- c("apple", "banana", "cherry", "apple"). Write R code to find and print the indices of all occurrences of the word "apple."

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
words <- c("apple", "banana", "cherry", "apple")
indices <- which(words == "apple")
print(indices)
```

#### Question 20: Conditional Capture

Assume you have a vector ages containing the ages of individuals. Write R code to extract and print the ages of individuals who are older than 30.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
ages <- c(32,12,43,9,44,30,18)
above_thirty <- ages[ages>30]
print(above_thirty)
```

#### Question 21: Extract Every Nth

Given a numeric vector sequence <- 1:20, write R code to extract and print every third element of the vector.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
sequence <- 1:20
every_third_element <- sequence[seq(from=1, to=20, by=3)]
print(every_third_element)
```

#### Question 22: Range Retrieval

Create a numeric vector numbers with values from 1 to 10. Write R code to extract and print the values between the fourth and eighth elements.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
numbers <- 1:10
print(numbers[4:8])
```

#### Question 23: Missing Matters

Suppose you have a numeric vector data <- c(10, NA, 15, 20). Write R code to check if the second element of the vector is missing (NA).

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
data <- c(10, NA, 15, 20)
print(is.na(data[2]))
```

#### Question 24: Temperature Extremes

Assume you have a numeric vector temperatures with daily temperatures. Create a logical vector hot_days that flags days with temperatures above 90 degrees Fahrenheit. Print the total number of hot days.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
daily_temperatures <- c(93,87,86,90,85,99,95,89,90)
hot_days <- daily_temperatures[daily_temperatures>90]
number_of_hot_days <- length(hot_days)
print(number_of_hot_days)
```

#### Question 25: String Selection

Given a character vector fruits containing fruit names, create a logical vector long_names that identifies fruits with names longer than 6 characters. Print the long fruit names.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
fruits <- c("apple", "banana", "pineapple", "strawberry", "raspberry", "grape", "blueberry")
long_names <- fruits[nchar(fruits) > 6]
print(long_names)
```

#### Question 26: Data Divisibility

Given a numeric vector numbers, create a logical vector divisible_by_5 to indicate numbers that are divisible by 5. Print the numbers that satisfy this condition.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
numbers <- c(12,10,24,25,36,30,75)
divisible_by_5 <- numbers %% 5 == 0
print(numbers[divisible_by_5])
```

#### Question 27: Bigger or Smaller?

You have two numeric vectors vector1 and vector2. Create a logical vector comparison to indicate whether each element in vector1 is greater than the corresponding element in vector2. Print the comparison results.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
vector1 <- c(140, 34, 25, 15, 30, 12)
vector2 <- c(5, 34, 20, 10, 25, 8)
comparison <- c(vector1 > vector2)
print(comparison)
```

